Notes of Quantum Field Theory in a Nutshell

### 2016-08-17 QFT/Notes of QFT in a Nutshell/Notes of QFT in a Nutshell.tex
Update notes about QFT in a nutshell.

The function $D(x)$ is also called a propagator. It "plays an 
essential role in quantum field theory. As the inverse of a
differential operator it is clearly closely related to the Green’s
function you encountered in a course on electromagnetism".

@@

This section tries to replicate the previous section's procedure to
produce a repulsive force. It starts with the Maxwell's Lagrangian for
electromagnetism $\mathcal{L}=-\frac{1}{4} F_{\mu\nu}F^{\mu\nu}$.
However, the authors adds an additional mass term and let the mass
$m\to 0$ in the end. This is declared to be avoiding the complication of
gauge invariance. The result is surprisingly simple. We have:
\begin{align}
    D_{\nu\lambda}(k)&=\frac{-g_{\nu\lambda}+k_\nu k_\lambda/m^2}
        {k^2-m^2}
    \nonumber\\
    W(J)&=\frac{1}{2} \int \frac{d^4k}{(2\pi)^4}
        J^\mu (k)^* \frac{1}{k^2-m^2+i\epsilon} J_\mu(k)
    \nonumber\\
    E&=\frac{1}{4\pi r}e^{-mr} 
\end{align}

This clearly represent the idea of repulsive Coulomb force.

\paragraph{Bypassing Maxwell}
% TODO stopped here.

\paragraph{Unclear Points} Marked in the book. Especially, where
in the calculatioin above shows that the field is of a spin $1$
or a spin $2$ meson?

>>>>

\nomenclature{$D(x)$}{propagator for the free field theory\nomrefpage}
The function $D(x)$ is also called a propagator. It "plays an 
essential role in quantum field theory. As the inverse of a
differential operator it is clearly closely related to the Green’s
function you encountered in a course on electromagnetism".

@@

This section tries to replicate the previous section's procedure to
produce a repulsive force. It starts with the Maxwell's Lagrangian for
electromagnetism $\mathcal{L}=-\frac{1}{4} F_{\mu\nu}F^{\mu\nu}$.
However, the authors adds an additional mass term and let the mass
$m\to 0$ in the end. This is declared to be avoiding the complication of
gauge invariance. The result is surprisingly simple. We have:
\begin{align}
    D_{\nu\lambda}(k)&=\frac{-g_{\nu\lambda}+k_\nu k_\lambda/m^2}
        {k^2-m^2}
        = \frac{-G_{\nu\lambda}}{k^2-m^2}
        \nomenclature{$D_{\nu\lambda}$}
            {Propagator for massive spin $1$ field\nomrefpage}
    \nonumber\\
    W(J)&=\frac{1}{2} \int \frac{d^4k}{(2\pi)^4}
        J^\mu (k)^* \frac{1}{k^2-m^2+i\epsilon} J_\mu(k)
    \nonumber\\
    E&=\frac{1}{4\pi r}e^{-mr} 
\end{align}
where he defines 
$G_{\nu\lambda}\equiv g_{\nu\lambda}-\frac{k_\nu k_\lambda}{m^2}$.
This clearly represent the idea of repulsive Coulomb force.

\paragraph{Bypassing Maxwell}

Here he re-evaluates the propagator for massive spin $1$ particle
(photon) using another approach, without the use of Maxwell's Lagrangian.
\footnote{
    In the appendix $1$, the author also provides a derivation of
    Maxwell's Lagrangian.
}
The calculation depends on that:
\begin{quote}
   The amplitude for a particle with momentum $k$ and polarization $a$
   to be created at the source is proportional to 
   $\varepsilon^{(a)}_\lambda(k)$, and the amplitude for it to be absorbed 
   at the sink is proportional to $\varepsilon^{(a)}_\lambda(k)$. We 
   multiply the amplitudes together to get the amplitude for
   propagation from source to sink, and then sum over the three 
   possible polarizations
\end{quote}
This should give the propagator. In the end, it is found that:
\begin{align}
    \sum_a \varepsilon^{(a)}_\nu(k) \varepsilon^{(a)}_\lambda(k)
    = - G_{\nu\lambda}(k) 
    \equiv - \left(g_{\nu\lambda}-\frac{k_\nu k_\lambda}{m^2}\right)
\end{align}

\paragraph{Bypassing Einstein}
% TODO stopped here.
\paragraph{Unclear Points} Marked in the book. Especially, where
in the calculatioin above shows that the field is of a spin $1$
or a spin $2$ meson?
